### 2023-11-08 manuscript/additional_files.Rmd
re-number additional files 4-6 inline with the restructuring of section 3.2

Additional file 4.csv - Table S7 -
The molecular formula assignments for *m/z* across all experimental matrices along with any match KEGG compound IDs.

Additional file 5.csv Table S8 -
The *m/z* features directly matched to predicted ionisation products of the spiked chemical compounds in urine.

Additional file 6.csv Table S9 -
The *m/z* features assigned to spiked chemical compounds in urine.

>>>>

Additional file 4.csv Table S7 -
The *m/z* features directly matched to theoretical ionisation products of the chemical standards in the standards mixed and spiked urine.

Additional file 5.csv Table S8 -
The *m/z* features assigned to chemical standards in the standards mix and spiked urine.

Additional file 6.csv - Table S9 -
The molecular formula assignments for *m/z* across all experimental matrices along with any match KEGG compound IDs.

### 2023-11-08 manuscript/manuscript.Rmd
re-number additional files 4-6 inline with the restructuring of section 3.2

To assess the performance of the molecular formula and graphical component selection approaches, the assignment outcomes were evaluated for the theoretical IPs calculated for the chemical standards that matched to *m/z* features in the standards mix and spiked urine. 
The standards mix allows for a direct evaluation of the selection approaches in a relatively simple, synthetic matrix.
Alternatively, the spiked urine provides an indication of how the selection approaches perform in a more realistic context where there are more *m/z* features present greater competition for assignment. 
To simplify interpretation, these evaluations were based on the assignment outcomes of the non-isotopic IPs during the adduct and isotopic assignment iterations.
This reduces the incidence of overlap between IPs, where multiple theoretical IPs match to a single *m/z* feature as well as a removes the inclusion of relationships involving transformations that complicates the calculation and interpretation of relevant relationships.
Based on the `r n_adducts` adduct rules specified, there were `r nrow(standards_assignment_outcomes_non_iso)` and `r nrow(spiked_urine_assignment_outcomes_non_iso)` theoretical IPs for these chemical standards that matched to `r n_features$standards` and `r n_features$spiked_urine` *m/z* in the standards mix and spiked urine respectively.
The theoretical IPs that directly matched *m/z* features, including the isotopic theoretical IPs, are provided in Additional file 5.
The frequencies of assignment outcomes for the theoretical IPs in these matrices are shown in Table \@ref(tab:ip-outcomes).

@@

The assignment results for the chemical standards in the standards mix and spiked urine are provided in Table \@ref(tab:compound-frequencies).
These show that, where compounds had *m/z* features matching to theoretical IPs, the approach was able to assign `r compounds_percent_assigned$standards`% and `r compounds_percent_assigned$spiked_urine`% of these chemical standards in the standards mix and spiked urine respectively. 
The *m/z* for which a chemical standard was assigned are provided in Additional file 6.

@@

An overview of the molecular formula assignments made across the example sample matrices is provided in Table S6 (Additional file 3).
All of the assignments for these example matrices along with any matched KEGG compound IDs are provided in Additional file 4.
The assignments obtained from the *B. distachyon* is provided as an example showing the intended real world application of the molecular formula assignment approach to a sample set that includes multiple underlying experimental classes in the correlation network.
A similar number of molecular formulas were assigned to the FIE-HRMS matrices for the spiked human urine and *B. distachyon* matrices as well as similar numbers of molecular formulas that were matched to KEGG compounds.

>>>>

To assess the performance of the molecular formula and graphical component selection approaches, the assignment outcomes were evaluated for the theoretical IPs calculated for the chemical standards that matched to *m/z* features in the standards mix and spiked urine. 
The standards mix allows for a direct evaluation of the selection approaches in a relatively simple, synthetic matrix.
Alternatively, the spiked urine provides an indication of how the selection approaches perform in a more realistic context where there are more *m/z* features present greater competition for assignment. 
To simplify interpretation, these evaluations were based on the assignment outcomes of the non-isotopic IPs during the adduct and isotopic assignment iterations.
This reduces the incidence of overlap between IPs, where multiple theoretical IPs match to a single *m/z* feature as well as a removes the inclusion of relationships involving transformations that complicates the calculation and interpretation of relevant relationships.
Based on the `r n_adducts` adduct rules specified, there were `r nrow(standards_assignment_outcomes_non_iso)` and `r nrow(spiked_urine_assignment_outcomes_non_iso)` theoretical IPs for these chemical standards that matched to `r n_features$standards` and `r n_features$spiked_urine` *m/z* in the standards mix and spiked urine respectively.
The theoretical IPs that directly matched *m/z* features, including the isotopic theoretical IPs, are provided in Additional file 4.
The frequencies of assignment outcomes for the theoretical IPs in these matrices are shown in Table \@ref(tab:ip-outcomes).

@@

The assignment results for the chemical standards in the standards mix and spiked urine are provided in Table \@ref(tab:compound-frequencies).
These show that, where compounds had *m/z* features matching to theoretical IPs, the approach was able to assign `r compounds_percent_assigned$standards`% and `r compounds_percent_assigned$spiked_urine`% of these chemical standards in the standards mix and spiked urine respectively. 
The *m/z* for which a chemical standard was assigned are provided in Additional file 5.

@@

An overview of the molecular formula assignments made across the example sample matrices is provided in Table S6 (Additional file 3).
All of the assignments for these example matrices along with any matched KEGG compound IDs are provided in Additional file 6.
The assignments obtained from the *B. distachyon* is provided as an example showing the intended real world application of the molecular formula assignment approach to a sample set that includes multiple underlying experimental classes in the correlation network.
A similar number of molecular formulas were assigned to the FIE-HRMS matrices for the spiked human urine and *B. distachyon* matrices as well as similar numbers of molecular formulas that were matched to KEGG compounds.
